Figures

### 2016-01-22 scripts/figures.Rmd
first 3 figs set

Here are the figures (or figure panels) we are thinking of using in the Benchmarking paper.  I will include my comments and decriptions on each and perhaps over time this will develop into the results section
```{r,settings_and_lib,echo=F,message=F,}
require(ggplot2)
require("plyr")
require("Biostrings")
require(reshape2)
require("pROC")
require(gridExtra)
require(cowplot)
require(gtable)
require(png)
theme_set(new = theme_classic())
require(knitr)
opts_chunk$set(fig.align = "center", warning = FALSE, echo = FALSE, fig.width = 10, 
    fig.height = 7,message=F,cache=T)

@@

### ROC skematic
```{r, roc_skematic}
set.seed(42) # make the figures reproducible
example<-data.frame(Condition=c(rep(x = c(TRUE,FALSE),each=20)),test=c(runif(20,-10,-4),runif(20,-6,0))) # Make a dataframe of T and F positives with random p values that favors a lower distribution for the TP
ex.roc<-roc(example$Condition~example$test) # make an ROC based on this data

@@

  #plot the roc
  roc.p<-ggplot(roc.df,aes(x=1-specificity,y=sensitivity))+geom_step(color="black",size=2)+xlab("1-Specificity")+ylab("Sensitivity")+theme(axis.title.y=element_text(vjust=1))
  roc.p<-roc.p+geom_line(data=lines,aes(x=spec,y=sense,color=as.factor(group)),size=c(1.5),lty=c(2))+scale_color_brewer(palette="Set1")

@@

 #plot the points and cut offs
 points.p<-ggplot(distribution,aes(x=1,y=test,fill=Condition))+geom_dotplot(binaxis = "y", stackdir = "center")+scale_fill_manual(values=c("white","black"),name="",breaks=c(T,F),labels=c("True Positive","False Positive"))+xlab("")+ylab("Log(p value)")+theme(axis.ticks = element_blank(), axis.text.x = element_blank(),axis.title.y = element_text(vjust=1.2))+xlab("")

 points.p<-points.p+geom_hline(yintercept=output$threshold,
                          size=1.5,lty=2,color=c("#e41a1c","#377eb8")) # these are the first 2 colors in set 1

 plot_grid(points.p, roc.p, labels=c("A", "B"), ncol = 2, nrow = 1)

@@

mutate(roc.df.adj,exp.freq=ifelse(test = grepl("0",exp.freq),yes=as.numeric(exp.freq)/1000,no = as.numeric(exp.freq)/100))->roc.df.adj
roc.df.adj<-roc.df.adj[order(roc.df.adj$exp.freq,decreasing = T),]
roc.table<-subset(roc.df.adj,select=c(gc,exp.freq,adj.sensitivity,TP,adj.specificity,FP))
return(roc.table)
}
```

@@

## Figure 2
```{r,Miseq_out_of_the_box}

@@

miseq.roc.p<-ggplot(m.roc.df,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols)+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))+theme(legend.position=c(0.8,.5))

@@

tbl<-tableGrob(m.roc.table,rows=NULL,theme=ttheme_minimal()) # Make table
tbl<-gtable_add_grob(tbl,
        grobs = segmentsGrob( # line across the bottom
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 2.0)),
        t = 1, b = 1, l = 1, r = ncol(tbl))

tbl<-gtable_add_grob(tbl,
        grobs = segmentsGrob( # line across the bottom
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(0,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 2.0)),
        t = 1, b = 1, l = 1, r = ncol(tbl))

@@

#plot_grid(miseq.setup,miseq.roc.p, tbl, labels=c("A", "B","C"), ncol = 3, nrow = 1)
# Figure 2
ggdraw() +
  draw_plot(miseq.setup, 0.01, .53, .45, .42) +
  draw_plot(miseq.roc.p, .5, .5, .45, .45) +
  draw_plot(tbl, 0, 0, 1, .5) +
  draw_plot_label(c("A", "B", "C"), c(0, 0.5, 0), c(1, 1, 0.5), size = 15)

@@

rm(list = setdiff(ls(), lsf.str())) # remove all variables except the functions

@@

### Hiseq expermintal setup

@@

```{r,hiseq_roc}
sum.df<-read.csv("../data/process/2015-6-23/Variants/all.sum.csv",stringsAsFactors = F,comment.char = "#") # reading in the variants from the pipeline output

@@

Hiseq.roc<-ggplot(subset(h.roc.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))+theme(legend.position="none")

@@

tbl<-tableGrob(h.table.df,rows=NULL,theme=ttheme_minimal()) # Make table

@@

ggdraw() +
  draw_plot(hiseq.setup, 0, .5, .5, .5) +
  draw_plot(Hiseq.roc, .5, .5, .5, .5) +
  draw_plot(tbl, 0, 0, 1, .5) +
  draw_plot_label(c("A", "B", "C"), c(0, 0.5, 0), c(1, 1, 0.5), size = 15)

@@

tbl<-tableGrob(h.cut.read.table.5,rows=NULL,theme=ttheme_minimal()) # Make table

@@

#knitr::kable(subset(lofreq.table,gc==5,select=c(exp.freq,TP,FP)))

tbl<-tableGrob(lofreq.table,rows=NULL,theme=ttheme_minimal()) # Make table

@@

tbl.4<-tableGrob(h.cut.read.table.4,rows=NULL,theme=ttheme_minimal()) # Make table

@@

tbl.3<-tableGrob(h.cut.read.table.3,rows=NULL,theme=ttheme_minimal()) # Make table

@@

tbl<-tableGrob(dups.table,rows=NULL,theme=ttheme_minimal()) # Make table

@@

This is so much better than before. 
### Concequences for diversity measurements

>>>>

Here are the figures (or figure panels) we are thinking of using in the Benchmarking paper.  I will include my comments and decriptions on each and perhaps over time this will develop into the results section
```{r,settings_and_lib,echo=F,message=F,}
require(ggplot2)
require("plyr")
require("Biostrings")
require(reshape2)
require("pROC")
require(gridExtra)
require(cowplot)
require(gtable)
require(png)
theme_set(new = theme_classic())
require(knitr)
opts_chunk$set(fig.align = "center", warning = FALSE, echo = FALSE,message=F,cache=F)

@@

### ROC skematic
```{r, roc_skematic,fig.height=5,fig.width=3.4}
set.seed(42) # make the figures reproducible
example<-data.frame(Condition=c(rep(x = c(TRUE,FALSE),each=20)),test=c(runif(20,-10,-4),runif(20,-6,0))) # Make a dataframe of T and F positives with random p values that favors a lower distribution for the TP
ex.roc<-roc(example$Condition~example$test) # make an ROC based on this data

@@

  #plot the roc
  roc.p<-ggplot(roc.df,aes(x=1-specificity,y=sensitivity))+geom_step(color="black",size=1.5)+xlab("1-Specificity")+ylab("Sensitivity")+theme(axis.title.y=element_text(vjust=1))
  roc.p<-roc.p+geom_line(data=lines,aes(x=spec,y=sense,color=as.factor(group)),size=c(1),lty=c(2))+scale_color_brewer(palette="Set1")

@@

 #plot the points and cut offs
 points.p<-ggplot(distribution,aes(x=1,y=test,fill=Condition))+geom_dotplot(binaxis = "y", stackdir = "center",dotsize = 1.5)+scale_fill_manual(values=c("white","black"),name="",breaks=c(T,F),labels=c("True Positive","False Positive"))+xlab("")+ylab("Log(p value)")+theme(axis.ticks = element_blank(), axis.text.x = element_blank(),axis.title.y = element_text(vjust=1.2),legend.position=c(0.8,0.6))+xlab("")

 points.p<-points.p+geom_hline(yintercept=output$threshold,
                          size=1,lty=2,color=c("#e41a1c","#377eb8")) # these are the first 2 colors in set 1

 plot_grid(points.p, roc.p, labels=c("A", "B"), ncol = 1, nrow = 2)

@@

mutate(roc.df.adj,exp.freq=ifelse(test = grepl("0",exp.freq),yes=as.numeric(exp.freq)/1000,no = as.numeric(exp.freq)/100))->roc.df.adj
roc.df.adj<-roc.df.adj[order(roc.df.adj$exp.freq,decreasing = T),]
roc.table<-subset(roc.df.adj,select=c(gc,exp.freq,adj.sensitivity,TP,adj.specificity,FP))
return(roc.table)
}

### tableGrob functions and settings #####
tt1<-ttheme_minimal(colhead=list(fg_params=list(fontface=1,cex=0.75,fontfamily="serif")),core=list(fg_params=list(cex=0.75,fontfamily="serif")))
make.table<-function(df,theme){
  tbl<-tableGrob(df,rows=NULL,theme=theme) # Make table
  tbl$widths <- unit(rep(1/ncol(tbl), ncol(tbl)), "npc")
  tbl<-gtable_add_grob(tbl,
        grobs = grobTree(
          segmentsGrob( # line across the bottom
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 2.0)),
        segmentsGrob( # line across the top
            x0 = unit(0,"npc"),
            y0 = unit(1,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(1,"npc"),
            gp = gpar(lwd = 2.0))),
        t = 1, b = 1, l = 1, r = ncol(tbl))

  tbl<-gtable_add_grob(tbl,
                     grobs=segmentsGrob(
                       x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 2.0)),
        t = nrow(tbl), b = nrow(tbl), l = 1, r = ncol(tbl))
}
```

@@

## Figure 2
```{r,Miseq_out_of_the_box,fig.width=7,fig.height=5}

@@

miseq.roc.p<-ggplot(m.roc.df,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.5%","1.25%","0.63%","0.016%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))+theme(legend.position=c(1,.5))

@@

tbl<-make.table(m.roc.table,tt1)

@@

#plot_grid(miseq.setup,miseq.roc.p, tbl, labels=c("A", "B","C"), ncol = 3, nrow = 1)
# Figure 2

ggdraw() +
  draw_plot(miseq.setup, 0.01, .1, 0.4, 0.8) + #x y width height
  draw_plot(miseq.roc.p, 0.43, 0.42, 0.5, 0.51) +
  draw_plot(tbl, 0.45, 0, 0.53, 0.47) +
  draw_plot_label(c("A", "B", "C"), c(0.01, 0.42, 0.42), c(0.78, 0.95, 0.46), size = 15)

pdf("../results/figures/miseq1.pdf",width=7,height=5)
ggdraw() +
  draw_plot(miseq.setup, 0.01, .1, 0.4, 0.8) + #x y width height
  draw_plot(miseq.roc.p, 0.43, 0.42, 0.5, 0.51) +
  draw_plot(tbl, 0.45, 0, 0.53, 0.47) +
  draw_plot_label(c("A", "B", "C"), c(0.01, 0.42, 0.42), c(0.78, 0.95, 0.46), size = 15)
dev.off()

@@

rm(list = setdiff(ls(), lsf.str())) # remove all variables except the functions
tt1<-ttheme_minimal(colhead=list(fg_params=list(fontface=1,cex=0.75,fontfamily="serif")),core=list(fg_params=list(cex=0.75,fontfamily="serif")))

@@

@@

```{r,hiseq_roc,fig.width=7,fig.height=5}
sum.df<-read.csv("../data/process/2015-6-23/Variants/all.sum.csv",stringsAsFactors = F,comment.char = "#") # reading in the variants from the pipeline output

@@

Hiseq.roc<-ggplot(subset(h.roc.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))+theme(legend.position="none")+theme(plot.margin=unit(c(0,0,0,0),"mm"))

@@

tbl<-make.table(h.table.df,tt1)    # Make table

@@

ggdraw() +
  draw_plot(hiseq.setup, 0, .1, 0.4, 0.8) + #x y width height
  draw_plot(Hiseq.roc, 0.43, 0.43, 0.5, 0.5) +
  draw_plot(tbl, 0.45, 0, 0.53, 0.47) +
  draw_plot_label(c("A", "B", "C"), c(0.05, 0.4, 0.42), c(0.95, 0.95, 0.46), size = 15)

pdf("../results/figures/hiseq1.pdf",width=7,height=5)
ggdraw() +
  draw_plot(hiseq.setup, 0, .1, 0.4, 0.8) + #x y width height
  draw_plot(Hiseq.roc, 0.43, 0.43, 0.5, 0.5) +
  draw_plot(tbl, 0.45, 0, 0.53, 0.47) +
  draw_plot_label(c("A", "B", "C"), c(0.05, 0.4, 0.42), c(0.95, 0.95, 0.46), size = 15)
dev.off()

@@

tbl<-make.table(h.cut.read.table.5,tt1) # Make table

@@

#knitr::kable(subset(lofreq.table,gc==5,select=c(exp.freq,TP,FP)))
lofreq.table<-subset(lofreq.table,gc==5,select=c(exp.freq,TP,FP))

tbl<-make.table(lofreq.table,tt1) # Make table

@@

tbl.4<-make.table(h.cut.read.table.4,tt1) # Make table

@@

tbl.3<-make.table(h.cut.read.table.3,tt1) # Make table

@@

tbl<-make.table(dups.table,tt1) # Make table

@@

This is so much better than before.
